---
title: 'Biosentinelle Report'
date: ''
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
params:
    nb_input: -1
    warning_collect: ""
---

\n\n<br><br>\n\n




[comment 1]: <> (The following script is used to be able to zoom on images)

<script>
  function toggleFullscreen(img) {
    if (img.classList.contains('fullscreen')) {
      img.classList.remove('fullscreen');
    } else {
      document.querySelectorAll('.fullscreen').forEach(el => el.classList.remove('fullscreen'));
      img.classList.add('fullscreen');
    }
  }
</script>
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>Images cliquables</title>
    <style>
        .image-container {
            display: flex;
            justify-content: space-around;
            gap: 10px;
        }
        .image-container img {
            width: 33%;
            cursor: pointer;
            transition: transform 0.3s ease;
        }
        .fullscreen {
            position: fixed;
            top: 0;
            left: 0;
            width: 100vw !important;
            height: 100vh !important;
            object-fit: contain;
            background: rgba(0, 0, 0, 0.9);
            z-index: 1000;
            transform: scale(1);
        }
    </style>
</head>

[comment 2]: <> (End of script to zoom on images)

[comment 3]: <> (The following script is meant to display the tsv files in a readable way)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

read_tsv_with_dummy <- function(file_path, nb){
    if( ! file.exists(file_path)){
        stop(paste0("\n\n================\n\nINTERNAL ERROR IN Print_report PROCESS.\nfile_path DOES NOT EXISTS: ", file_path, "\n\nPLEASE, REPORT AN ISSUE HERE https://gitlab.pasteur.fr/gmillot/repertoire_profiler/-/issues OR AT gael.millot<AT>pasteur.fr.\n\n========\n\n"), call. = FALSE)
    }else if(file.info(file_path)$size == 0){
        stop(paste0("\n\n================\n\nINTERNAL ERROR IN Print_report PROCESS.\nfile_path FILE IS EMPTY BUT SHOULD NOT BE READ HERE. PATH IS: ", file_path, "\n\nPLEASE, REPORT AN ISSUE HERE https://gitlab.pasteur.fr/gmillot/repertoire_profiler/-/issues OR AT gael.millot<AT>pasteur.fr.\n\n========\n\n"), call. = FALSE)
    }else{
        df <- read.table(file_path, header = TRUE, sep = "\t", fill = TRUE, quote = "", comment.char = "", stringsAsFactors = FALSE)
        truncated <- FALSE
        # If the file is empty but has column names, add an empty line to make the column names readable
        if (nrow(df) == 0){
            dummy_row <- as.data.frame(matrix("", nrow = 1, ncol = ncol(df)))
            colnames(dummy_row) <- colnames(df)
            df <- df[ -(1:nrow(df)), ]
        }else if(nrow(df) > nb){
            df <- df[1:nb, ]
            truncated <- TRUE
        }
        return(list(df = df, truncated = truncated, nb = nb))
    }
}
```

<style>
details.inline {display:inline-block;}
</style>

[comment 4]: <> (End tsv display)

[comment 5]: <> (Openable .config file)

```{r echo=FALSE, results='hide'}
txt <- readLines("./config_file.txt", warn = FALSE)
# basic HTML-escaping so config symbols display correctly
escape <- function(x) {
  x <- gsub("&", "&amp;", x, fixed = TRUE)
  x <- gsub("<", "&lt;",  x, fixed = TRUE)
  x <- gsub(">", "&gt;",  x, fixed = TRUE)
  x
}
out <- c(
  "<!doctype html>",
  "<meta charset='utf-8'>",
  "<title>nextflow.config</title>",
  "<pre style='white-space:pre; font-family:monospace;'>",
  escape(txt),
  "</pre>"
)
writeLines(out, "nextflow.config.html")
``` 

[comment 6]: <> (end Openable .config file)

[comment 7]: <> (assignation of params, for later reassignation)

```{r, echo=FALSE, results='asis'}
    nb_input <- params$nb_input
    warning_collect <- params$warning_collect
```

[comment 8]: <> (end assignation of params, for later reassignation)


Description of the folders and files can be found [here](https://github.com/biosentinelle/biosentinelle/tree/main#output)
<br>
The <i>[nextflow.config](./reports/nextflow.config.html)</i> file mentioned here is the one gathering all the parameters set for the present analysis. A copy is saved in the [reports](./reports) folder.
<br><br>

### Most probable strain (by alignment)

Number of reference genomes tested : ```r nb_input```

The table below indicates the number of variants compared to the indicated genome of reference.<br>
The top one is the most probable background of the tested strain:

```{r, echo=FALSE, results='asis'}
        cat(paste0('
&nbsp; <details class="inline"><summary style="color: #1a73e8; font-family: Arial, sans-serif; font-size: 1em; font-weight: bold;">view</summary>
<span style="color:green">snp_counts.tsv file in the [tsv](./tsv) folder</span>
        '))
        tempo_read <- read_tsv_with_dummy("tsv/snp_counts.tsv", 3)
        df <- tempo_read$df
        truncated_log <- tempo_read$truncated
        if(is.data.frame(df) && truncated_log){
            cat(paste0('<span style="color:green;font-style:italic;">(table truncated to ', tempo_read$nb, ' rows in the display):</span><br><br>'))
        }else{
            cat('<span style="color:green;font-style:italic;">:</span><br><br>')
        }
        cat(knitr::kable(df, format = "html", row.names = FALSE))
        cat('
<br>
</details>
        ')
```

### Features found (by alignment)

Number of features tested : ```r nb_input```

The table below indicates the max and mean coverage, meaning nb of reads covering the tested features:

```{r, echo=FALSE, results='asis'}
        cat(paste0('
&nbsp; <details class="inline"><summary style="color: #1a73e8; font-family: Arial, sans-serif; font-size: 1em; font-weight: bold;">view</summary>
<span style="color:green">coverage.tsv file in the [tsv](./tsv) folder</span>
        '))
        tempo_read <- read_tsv_with_dummy("tsv/coverage.tsv", 3)
        df <- tempo_read$df
        truncated_log <- tempo_read$truncated
        if(is.data.frame(df) && truncated_log){
            cat(paste0('<span style="color:green;font-style:italic;">(table truncated to ', tempo_read$nb, ' rows in the display):</span><br><br>'))
        }else{
            cat('<span style="color:green;font-style:italic;">:</span><br><br>')
        }
        cat(knitr::kable(df, format = "html", row.names = FALSE))
        cat('
<br>
</details>
        ')
```

###  Backup

See the [reports](./reports) folder for all the details of the analysis, including:<br><ul><li>**nextflow.config** Parameter settings.<br></li><li>**Run_info.txt** Variables.<br></li><li>**trace.txt** and **timeline.html** Date of execution, CPU% and Memory requirement for each step.<br></ul>

```{r include = FALSE}
#remove work directory from current directory
wd <- getwd()
parts <- unlist(strsplit(wd, "/"))
path <- paste(parts[1:(length(parts) - 3)], collapse = "/")
path <- paste0(path, "/")
```
Warning: the full .nextflow.log is in: ```r path```. Indeed, the one in the [reports](./reports) folder is not complete (miss the end).


<br><br>

<style>
  #TOC { max-width: 200px !important;}
  /* .tocify-item { font-size: 100% !important; } */
</style>

<style> 
  body .container, body .container-fluid { max-width: 90% !important; width: 100% !important; margin: 0 auto;  } 
</style>

<style>
  .toc-content.col-xs-12.col-sm-8.col-md-9 { margin-left: 10px !important; padding-left: 0 !important; } 
</style>

<style> /* Force a fixated width, float left and add space on the right */ .col-xs-12.col-sm-4.col-md-3 { width: 250px !important; float: left; margin-right: 20px; /* reduce interior margin */ padding: 5px; } </style>
